---
title: "Final Project - Portfolio"
author: "Tamara Niella"
date: "February 27, 2019"
output: html_document
---


```{r setup, include=FALSE}

library(aod)
library(ggplot2)
library(here)
library(tidyverse)
library(rio)
library(magrittr)
library(skimr)
library(janitor)
library(fastDummies)
library(reshape2)
library(wesanderson)
library(ggridges)

knitr::opts_chunk$set(echo = TRUE)

```

```{r data_wrangling}
#Load data 


dat_int<- import(here("Data", "sim_data_int.csv"))

#making variable names nice 

colnames(dat_int)[1]<- "mindset"

dat_int%<>% janitor::clean_names()

#getting rid of subjects that in the expeirment had some kind of problem (did't complete task well etc), and I am only keeping data from one participant per dyad, since initially, I will only look at answers that dyads answered together (same answer for both participants, I only need one)

dat_dyad<- dat_int%>% 
  filter(problem==0, dyad_part== "A") 

#getting demographic data (for potential methods section)

dat_dem<- dat_int%>% 
  filter(problem==0, gender>0)%>%
  drop_na(age)%>%
  select(gender, age)

mean_age <- mean(dat_dem$age)
sd_age <- sd(dat_dem$age)
sum_fem <- dat_dem %>% 
  filter(gender==2)%>%
  summarize(fem = length(gender))

sum_dem <- dat_dem %>% 
  group_by(gender)%>%
  summarize(gen = length(gender))

#renaming variable value names, changing "treatment for doubt", to improve explanation of study through graphs and analysis

dat_dyad$mindset <-  gsub("Treatment", "Doubt", dat_dyad$mindset)

#coding mindset as factor 

dat_dyad$mindset<-  as.factor(dat_dyad$mindset)
```


#Plot 1

A bar graph comparing the proportion of agreement (y-axis) between the participants who had the “control” mindset and the participants who got the “doubt” mindset (x- axis, 1 bar per group).
The goal would be to communicate the effect of the mindset on the chances of reaching an agreement. 


```{r plot1}
#I want to see the dyad aswers for agreement (yes or no) for both stories, then I will create a new data set with one variable for agreement, that will iclude agreement for stories one and 2 and another variable that will indicate whether that agreement belongs to story 1 (freedom of speech) or 2 (cyber privacy)

mindset2 <- rep(dat_dyad$mindset, 2)
agreement <- c(dat_dyad$dyad_ag_s1, dat_dyad$dyad_ag_s2)
story <- as.factor(c(rep.int(1,36), rep.int(2,36)))


data<- data.frame(mindset2, agreement, story)

#change values of variable "story", names for numbers (I will only need this if I decide to show the proportions of agreement for the different stories - which is not totally relevant to the results of the study, so I am still debating about it )

data$story <- gsub("1", "Freedom of Speech", data$story)
data$story <- gsub("2", "Cyber Privacy", data$story)

#try 1: summarizing data for plot 1 (version dividing agreement not only per mindset but also per story)

summary2<- data%>% 
  group_by(mindset2, story)%>%
  summarize(prop_agreement =round(mean(agreement),2))
summary2%<>% rename("Mindset" = mindset2)

#try 2: summarizing data for plot 1 (version dividing agreement only per mindset)

summary3<- data%>% 
  group_by(mindset2)%>%
  summarize(prop_agreement =round(mean(agreement),2))


#try 1: plot 1 (including stories division)

ggplot(summary2, aes(story, prop_agreement))+
  geom_col(aes(fill=Mindset), position = "dodge", alpha=.7)+
  scale_fill_manual(values=wes_palette(name="Moonrise2", n=2))+
  labs(title= "Proportion of agreement in Control vs Doubt, by Story", x = "Story", y = "Proportion of agreement")+
  theme_minimal()

#try 2: plot 1 (without including stories division)

ggplot(summary3, aes(mindset2, prop_agreement))+
  geom_col(alpha=.7, fill = c("#798E87", "#C27D38"),width = .6)+
  labs(title= "Proportion of agreement in Control vs Doubt groups", x = "Mindset", y = "Proportion of agreement") + 
  theme_minimal() 


```

#Plot 2

A bar graph comparing the proportion of agreement (y-axis) between the interaction condition (interaction agreement) and the imagine condition (imagine agreement) - x- axis, 1 bar per group-.
The goal would be to communicate whether participant’s expectancy of agreement is different to the actual proportion of agreement when participants have a real interaction face-to-face.


```{r}

#data set up

imagine <- import(here("data", "sim_data_im.csv"))
data_im <- data.frame(imagine$s1_agrement_y_n, imagine$s2_agrement_y_n)

colnames(data_im)<- c("agreement_1im", "agreement_2im")

agreement_im <- c(data_im$agreement_1im, data_im$agreement_2im)
stories_im <- c(rep("Freedom of Speech", 34), rep("Cyber Privacy", 34) )
data_im_long <- data.frame(agreement_im, stories_im)

agreement_all <- c(agreement, agreement_im)
condition <- as.factor(c(rep.int("interaction",72), rep.int("imagine",68)))
stories_all <- as.factor(c(data$story, stories_im))

data_in_im <- data.frame(agreement_all, condition, stories_all)

#summary of proportions of agreement in imagine and interaction for plot 2 

summary_cond<- data_in_im%>% 
  group_by(condition)%>%
  summarize(prop_agreement =mean(agreement_all))

#plot 2 - version without dividing by stories 

ggplot(summary_cond, aes(condition, prop_agreement))+
  geom_col(alpha=.7, fill = c("#F1BB7B", "#FD6467"),width = .6)+
  labs(title= "Agreement in Interaction  vs Expected agreement in Imagine", x = "Condition", y = "Proportion of agreement")+
  theme_minimal()+
  ylim(0, 1)

#summary of proportions of agreement in imagine and interaction for plot 2 - version dividing by story 

summary_cond_s<- data_in_im%>% 
  group_by(condition, stories_all)%>%
  summarize(prop_agreement =mean(agreement_all))

#plot 2 - version dividing by stories 

ggplot(summary_cond_s, aes(stories_all, prop_agreement))+
  geom_col(aes(fill=condition), position = "dodge", alpha=.7)+
  scale_fill_manual(values=wes_palette(name="GrandBudapest1", n=2))+
  labs(title= "Agreement in Interaction  vs Expected agreement in Imagine, by Story", x = "Story", y = "Proportion of agreement")+
  theme_minimal()

```

#Plot 3 

I want to compare the variation in Judgement from Part 1 to Part 3 (∆Judgment1-3) between the 2 different mindset groups. 

This could be represented using histograms with ggridges , where we would have an histogram of Judgment Part and Judgment Part 3 for the Control group and another for the Doubt group. 

I am still trying to think what is the best way of representing this. A line graph with mean differences could also be good representation. 

The goal would be to communicate the effect of the mindset participants are given, in how much their own opinion on a moral or political issue changes after discussing it with someone else. 

```{r}

```


