---
title: "Final Project - Portfolio"
author: "Tamara Niella"
date: "February 27, 2019"
output: html_document
---


```{r setup, include=FALSE}

library(aod)
#install.packages("aod")
library(ggplot2)
library(here)
library(tidyverse)
library(rio)
library(magrittr)
library(skimr)
library(janitor)
library(fastDummies)
#install.packages("fastDummies")
library(reshape2)
library(wesanderson)
library(ggridges)

knitr::opts_chunk$set(echo = TRUE)

```

The data wrangling seemed straightforward and all had a purpose! I added spaces between some of the code (before and after "=" and pipes) to it's easier to read. I've never used or seen the use of "gsub" before, interesting way to rename variables!
```{r data_wrangling}
#Load data 

dat_int<- import(here("Data", "sim_data_int.csv"))

#making variable names nice 

colnames(dat_int)[1]<- "mindset"

dat_int %<>% janitor::clean_names()

#getting rid of subjects that in the expeirment had some kind of problem (did't complete task well etc), and I am only keeping data from one participant per dyad, since initially, I will only look at answers that dyads answered together (same answer for both participants, I only need one)

dat_dyad<- dat_int %>% 
  filter(problem == 0, dyad_part == "A") 

#getting demographic data (for potential methods section)

dat_dem<- dat_int %>% 
  filter(problem == 0, gender > 0) %>%
  drop_na(age) %>%
  select(gender, age)

mean_age <- mean(dat_dem$age)
sd_age <- sd(dat_dem$age)
sum_fem <- dat_dem %>% 
  filter(gender == 2 )%>%
  summarize(fem = length(gender))

sum_dem <- dat_dem %>% 
  group_by(gender) %>%
  summarize(gen = length(gender))

#renaming variable value names, changing "treatment for doubt", to improve explanation of study through graphs and analysis

dat_dyad$mindset <-  gsub("Treatment", "Doubt", dat_dyad$mindset)

#coding mindset as factor 

dat_dyad$mindset <- as.factor(dat_dyad$mindset)
```


#Plot 1

A bar graph comparing the proportion of agreement (y-axis) between the participants who had the “control” mindset and the participants who got the “doubt” mindset (x- axis, 1 bar per group).
The goal would be to communicate the effect of the mindset on the chances of reaching an agreement. 


```{r plot1}
#I want to see the dyad aswers for agreement (yes or no) for both stories, then I will create a new data set with one variable for agreement, that will iclude agreement for stories one and 2 and another variable that will indicate whether that agreement belongs to story 1 (freedom of speech) or 2 (cyber privacy)

mindset2 <- rep(dat_dyad$mindset, 2)
agreement <- c(dat_dyad$dyad_ag_s1, dat_dyad$dyad_ag_s2)
story <- as.factor(c(rep.int(1,36), rep.int(2,36)))


data<- data.frame(mindset2, agreement, story)

#change values of variable "story", names for numbers (I will only need this if I decide to show the proportions of agreement for the different stories - which is not totally relevant to the results of the study, so I am still debating about it )

data$story <- gsub("1", "Freedom of Speech", data$story)
data$story <- gsub("2", "Cyber Privacy", data$story)

#try 1: summarizing data for plot 1 (version dividing agreement not only per mindset but also per story)

summary2<- data%>% 
  group_by(mindset2, story)%>%
  summarize(prop_agreement =round(mean(agreement),2))
summary2%<>% rename("Mindset" = mindset2)

#try 2: summarizing data for plot 1 (version dividing agreement only per mindset)

summary3<- data%>% 
  group_by(mindset2)%>%
  summarize(prop_agreement =round(mean(agreement),2))


#try 1: plot 1 (including stories division)

ggplot(summary2, aes(story, prop_agreement))+
  geom_col(aes(fill=Mindset), position = "dodge", alpha=.7)+
  scale_fill_manual(values=wes_palette(name="Moonrise2", n=2))+
  labs(title= "Proportion of agreement in Control vs Doubt, by Story", x = "Story", y = "Proportion of agreement")+
  theme_minimal()

#try 2: plot 1 (without including stories division)

ggplot(summary3, aes(mindset2, prop_agreement))+
  geom_col(alpha=.7, fill = c("#798E87", "#C27D38"),width = .6)+
  labs(title= "Proportion of agreement in Control vs Doubt groups", x = "Mindset", y = "Proportion of agreement") + 
  theme_minimal() 


```
Thoughts for plot 1:
I think I actually like try 1 (including the story division)! You have a lot of good features in this plot! I like the use of theme minimal and alpha to see the lines behind the bars. The label axes and title are clear! My suggestion for this plot would be to increase the font size for the axes labels. You could also overlay the individual data points on the bars to show the distribution of data. I'm also curious if there's a group difference in the cyber privacy story by mindset!

#Plot 2

A bar graph comparing the proportion of agreement (y-axis) between the interaction condition (interaction agreement) and the imagine condition (imagine agreement) - x- axis, 1 bar per group-.
The goal would be to communicate whether participant’s expectancy of agreement is different to the actual proportion of agreement when participants have a real interaction face-to-face.


```{r}

#data set up

imagine <- import(here("data", "sim_data_im.csv"))
data_im <- data.frame(imagine$s1_agrement_y_n, imagine$s2_agrement_y_n)

colnames(data_im)<- c("agreement_1im", "agreement_2im")

agreement_im <- c(data_im$agreement_1im, data_im$agreement_2im)
stories_im <- c(rep("Freedom of Speech", 34), rep("Cyber Privacy", 34) )
data_im_long <- data.frame(agreement_im, stories_im)

agreement_all <- c(agreement, agreement_im)
condition <- as.factor(c(rep.int("interaction",72), rep.int("imagine",68)))
stories_all <- as.factor(c(data$story, stories_im))

data_in_im <- data.frame(agreement_all, condition, stories_all)

#summary of proportions of agreement in imagine and interaction for plot 2 

summary_cond<- data_in_im%>% 
  group_by(condition)%>%
  summarize(prop_agreement =mean(agreement_all))

#plot 2 - version without dividing by stories 

ggplot(summary_cond, aes(condition, prop_agreement))+
  geom_col(alpha=.7, fill = c("#F1BB7B", "#FD6467"),width = .6)+
  labs(title= "Agreement in Interaction  vs Expected agreement in Imagine", x = "Condition", y = "Proportion of agreement")+
  theme_minimal()+
  ylim(0, 1)

#summary of proportions of agreement in imagine and interaction for plot 2 - version dividing by story 

summary_cond_s<- data_in_im%>% 
  group_by(condition, stories_all)%>%
  summarize(prop_agreement =mean(agreement_all))

#plot 2 - version dividing by stories 

ggplot(summary_cond_s, aes(stories_all, prop_agreement))+
  geom_col(aes(fill=condition), position = "dodge", alpha=.7)+
  scale_fill_manual(values=wes_palette(name="GrandBudapest1", n=2))+
  labs(title= "Agreement in Interaction vs Expected agreement in Imagine, by Story", x = "Story", y = "Proportion of agreement")+
  theme_minimal()

```
Thoughts on plot 2:
For this plot I also like the division by story and condition! It's really interesting how height the proportion of agreement is when they actually interaction- pretty cool! I really like the colors (although they might not be color blind safe). I think for this one it would also be nice to see the individual data points and the data distribution! It might also be helpful to make the y axis percent agreement and multiple by 100. For me it's easier to think in percent rather than proportion (even though it's the same thing)! It would also clean up the y axis a little!

#Plot 3 

I want to compare the distribution of Judgement from Part 1 to Part 3 between the 2 different mindset groups >> to see whether the sample becomes or or less polarized after discussion depending to what mindset group they belonged

This could be represented using histograms  , where we would have an histogram of Judgment Part 1 and Judgment Part 3 for the Control group and another for the Doubt group. 

I am still trying to think what is the best way of representing this. A line graph with mean differences could also be good representation. 

The goal would be to communicate the effect of the mindset that is given to participants, in how much their own opinion on a moral or political issue changes after discussing it with someone else, and whether people get closer in opinion or not. 

 THE PLOT(S) FOR THIS CREATED AS OF 02.27.2019 ARE VERY VERY PRELIMINARY - it took me a long while to figure out what the best way to look at this data is, and I am still not sure if this is the right one
 
```{r}

#I am going to focus on data from the interaction condition and for this I will look at individual data (Parts 1 and 3 were done individually, not in pairs)

data_ok <- dat_int %>% filter(problem==0)
data_ok$mindset <-  gsub("Treatment", "Doubt", data_ok$mindset)

mindset3 <- rep(data_ok$mindset, 4)

judge_p1 <- c(data_ok$s1_judge_p1, data_ok$s2_judge_p1)
judge_p3 <- c(data_ok$s1_judge_p3, data_ok$s2_judge_p3)
judge <- c(judge_p1, judge_p3)
story3 <- rep(as.factor(c(rep.int(1,92), rep.int(2,92))),2)
part <-as.factor(c(rep.int(1,184), rep.int(3,184)))


data_3<- data.frame(mindset3, judge, story3,part)

data_3$story3 <- gsub("1", "Freedom of Speech", data_3$story3)
data_3$story3 <- gsub("2", "Cyber Privacy", data_3$story3)

data_3 %<>% drop_na(judge)

#Plot 3 for doubt mindset 

data_3 %>% filter(mindset3== "Doubt")%>%
ggplot(aes(judge))+
  geom_histogram()+
  facet_wrap(~part)

#plot 3 for control mindset 

data_3 %>% filter(mindset3== "Control")%>%
ggplot(aes(judge))+
  geom_histogram()+
  facet_wrap(~part)

#just thinking about what density plot might look like with your data 
data_3 %>% filter(mindset3== "Control")%>%
ggplot(aes(judge, color = part, fill = part))+
  geom_density(alpha = 0.5)+
  theme_minimal()


```
Plot 3 thoughts: 
I think you could try and use a density plot here and overlay the two different distributions (doubt and control mindset)! I added an example above for the control condition and overlay part 1 and 3. You might have to play with it a bit, but I think density plots look a little better than histograms! I know this is a rough draft but it'll be impotant to label the x axis so that it's descriptive! You have a good start though.

